---
title: ""
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: false
geometry: margin=0.75in, landscape
header-includes:
  - \usepackage{graphicx}
  - \usepackage{xcolor}
  - \usepackage{tikz}
  - \usetikzlibrary{shapes.geometric}
  - \pagenumbering{gobble}
  - \usepackage[T1]{fontenc}
  - \setmainfont{Latin Modern Roman}
params:
  name: "Paulo Cesar Alamos Muñoz"
  rut: "15.450.224-6"
  cargo: "Técnico Mecánico"
  empresa: "Tecnologías Cobra"
  course: "Capacitacion de Habilidades"
  date: "nov 10, 2025 at 01:58a. m. UTC"
  hora: "05:00pm"
  duration: "1 hora 3 minutos"
  skill1: "Herramientas de IA generativa"
  skill2: "Inteligencia artificial"
  skill3: "IA generativa"
  skill4: ""
  skill5: ""
  skill6: ""
  instructor: "Dominique, directora de formación global"
  instructor_name: "Dominique"
  # cert_id: "975cd32fc40a721d4983cc8119daf41d0c1661f3fc1725355bc8ea570a32b917"
  qr_path: ""
  logo_path: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Collect non-empty skills into a list
skills <- c(params$skill1, params$skill2, params$skill3, 
            params$skill4, params$skill5, params$skill6)
skills <- skills[skills != ""]
num_skills <- length(skills)
```

\begin{center}

% \vspace*{0.5cm}

% 1. Save the logo width to a length variable
\newlength{\logowidth}
\settowidth{\logowidth}{\includegraphics[height=1.5cm]{images/merc_720.png}}

% Company Logo - Image from www folder
\includegraphics[height=1.5cm]{images/merc_720.png}

% 3. Display CONSULTORA stretched to that exact width
\begin{tikzpicture}
% We use resizebox to stretch/shrink the text to \logowidth
\node[inner sep=0pt] (consultora) {
    \resizebox{\logowidth}{!}{%
        \textbf{\textcolor{gray!70}{CONSULTORA}}%
    }
};

% Draw the lines using the node boundaries
\draw[gray!50, line width=0.5pt] ([yshift=2pt]consultora.north west) -- ([yshift=2pt]consultora.north east);
\draw[gray!50, line width=0.5pt] ([yshift=-2pt]consultora.south west) -- ([yshift=-2pt]consultora.south east);
\end{tikzpicture}

\vspace{0.8cm}

% Title
{\fontsize{32}{38}\selectfont \textbf{`r params$course`}}

\vspace{0.8cm}

% Completion text
{\fontsize{16}{20}\selectfont Capacitación realizada a \textbf{`r params$name`} (`r params$rut`)}

\vspace{0.2cm}

{\fontsize{16}{20}\selectfont \textbf{`r params$cargo`} - \textbf{`r params$empresa`}.}

\vspace{0.4cm}

{\fontsize{13}{16}\selectfont `r params$date`, a las `r params$hora` - `r params$duration`.}

\vspace{0.8cm}

% Skills section - only show if there are skills
```{r skills-section, results='asis'}
if (num_skills > 0) {
  cat("% Skills badges\n")
  cat("\\vspace{0.3cm}\n\n")
  
  # Generate TikZ code for skills badges
  cat("\\begin{tikzpicture}\n")
  
  # Calculate positions for badges - centered layout
  # Arrange in rows of up to 3 badges each
  x_positions <- c(0, 5.5, 10.5)  # x positions for up to 3 badges per row
  
  for (i in seq_along(skills)) {
    row <- ceiling(i / 3) - 1  # 0-indexed row
    col <- ((i - 1) %% 3) + 1  # 1-indexed column position
    
    x_pos <- x_positions[col]
    y_pos <- -row * 1.2  # each row is 1.2cm below the previous
    
    # Escape special LaTeX characters in skill text
    skill_text <- gsub("&", "\\\\&", skills[i])
    skill_text <- gsub("%", "\\\\%", skill_text)
    skill_text <- gsub("_", "\\\\_", skill_text)
    
    # Calculate minimum width based on longest skill text (approx 0.2cm per char)
    max_chars <- max(nchar(skills))
    min_width <- paste0(round(max_chars * 0.22, 1), "cm")
    
    cat(sprintf("\\node[draw=gray!50, rounded corners=12pt, inner xsep=12pt, inner ysep=6pt, line width=1pt, align=center, minimum width=%s] at (%s,%s) {%s};\n",
                min_width, x_pos, y_pos, skill_text))
  }
  
  cat("\\end{tikzpicture}\n\n")
  
  cat("\\vspace{0.8cm}\n")
} else {
  cat("\\vspace{0.5cm}\n")
}
```

\vspace{0.8cm}

% Bottom section - QR code and validation text centered
\vfill

\noindent
\begin{minipage}[b]{\textwidth}
\centering
% QR Code and validation text
\begin{tabular}{@{}c@{\hspace{0.5cm}}c@{}}
$\vcenter{\hbox{\includegraphics[height=2.5cm]{`r params$qr_path`}}}$ & 
\begin{minipage}[c][2.5cm][c]{0.55\textwidth}
\centering
{\fontsize{13}{16}\selectfont Este certificado cuenta con validación digital. \\Para verificar su autenticidad, escanee el código QR.}
\end{minipage}
\end{tabular}
\end{minipage}

\vspace{0.8cm}

% Footer - centered on full page
{\fontsize{9}{11}\selectfont MERC Consultora Limitada - Consultoría y Servicios Profesionales}

{\fontsize{9}{11}\selectfont MERCCONSULTORA.CL}

\end{center}

\begin{tikzpicture}[remember picture, overlay]
% Sello image - positioned in absolute bottom right corner
\node[anchor=south east, xshift=-1cm, yshift=1cm] at (current page.south east) {
  \includegraphics[height=3.5cm]{images/sello_certificado.png}
};
\end{tikzpicture}
